\begin{TabularC}{7}
\hline
\rowcolor{lightgray}{\bf Sr. No. }&{\bf Rule I\-D }&{\bf Title }&{\bf Category }&{\bf Enabled }&{\bf Code\-Fix }&{\bf Description  }\\\cline{1-7}
1 &\href{https://docs.microsoft.com/visualstudio/code-quality/ca1058-types-should-not-extend-certain-base-types}{\tt C\-A1058} &Types should not extend certain base types &Design &True &True &An externally visible type extends certain base types. Use one of the alternatives. \\\cline{1-7}
2 &\href{https://docs.microsoft.com/visualstudio/code-quality/ca2153-avoid-handling-corrupted-state-exceptions}{\tt C\-A2153} &Do Not Catch Corrupted State Exceptions &Security &True &False &Catching corrupted state exceptions could mask errors (such as access violations), resulting in inconsistent state of execution or making it easier for attackers to compromise system. Instead, catch and handle a more specific set of exception type(s) or re-\/throw the exception \\\cline{1-7}
3 &\href{https://docs.microsoft.com/visualstudio/code-quality/ca3075-insecure-dtd-processing}{\tt C\-A3075} &Insecure D\-T\-D processing in X\-M\-L &Security &True &False &Using Xml\-Text\-Reader.\-Load(), creating an insecure Xml\-Reader\-Settings instance when invoking Xml\-Reader.\-Create(), setting the Inner\-Xml property of the Xml\-Document and enabling D\-T\-D processing using Xml\-Url\-Resolver insecurely can lead to information disclosure. Replace it with a call to the Load() method overload that takes an Xml\-Reader instance, use Xml\-Reader.\-Create() to accept Xml\-Reader\-Settings arguments or consider explicitly setting secure values. The Data\-View\-Setting\-Collection\-String property of Data\-View\-Manager should always be assigned from a trusted source, the Dtd\-Processing property should be set to false, and the Xml\-Resolver property should be changed to Xml\-Secure\-Resolver or null.\-  \\\cline{1-7}
4 &\href{https://docs.microsoft.com/visualstudio/code-quality/ca3076-insecure-xslt-script-execution}{\tt C\-A3076} &Insecure X\-S\-L\-T script processing. &Security &True &False &Providing an insecure Xslt\-Settings instance and an insecure Xml\-Resolver instance to Xsl\-Compiled\-Transform.\-Load method is potentially unsafe as it allows processing script within X\-S\-L, which on an untrusted X\-S\-L input may lead to malicious code execution. Either replace the insecure Xslt\-Settings argument with Xslt\-Settings.\-Default or an instance that has disabled document function and script execution, or replace the Xml\-Resolver argurment with null or an Xml\-Secure\-Resolver instance. This message may be suppressed if the input is known to be from a trusted source and external resource resolution from locations that are not known in advance must be supported. \\\cline{1-7}
5 &\href{https://docs.microsoft.com/visualstudio/code-quality/ca3077-insecure-processing-in-api-design-xml-document-and-xml-text-reader}{\tt C\-A3077} &Insecure Processing in A\-P\-I Design, Xml\-Document and Xml\-Text\-Reader &Security &True &False &Enabling D\-T\-D processing on all instances derived from Xml\-Text\-Reader or  \-Xml\-Document and using Xml\-Url\-Resolver for resolving external X\-M\-L entities may lead to information disclosure. Ensure to set the Xml\-Resolver property to null, create an instance of Xml\-Secure\-Resolver when processing untrusted input, or use Xml\-Reader.\-Create method with a secure Xml\-Reader\-Settings argument. Unless you need to enable it, ensure the Dtd\-Processing property is set to false.\-  \\\cline{1-7}
6 &\href{https://docs.microsoft.com/visualstudio/code-quality/ca3147-mark-verb-handlers-with-validateantiforgerytoken}{\tt C\-A3147} &Mark Verb Handlers With Validate Antiforgery Token &Security &True &False &Missing Validate\-Anti\-Forgery\-Token\-Attribute on controller action \{0\}. \\\cline{1-7}
\end{TabularC}
